Mbh-n paper

### 2015-10-23 papers/mbhn/mbhn.tex
friday suzuki

\section{Data}
We populated the $M_{\rm BH} - n_{\rm sph}$ diagram with the same galaxy sample used in \emph{Paper II}, 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii 
(see Savorgnan \& Graham 2015 for a discussion on this topic).

%%%
Spheroid magnitudes were derived from our state-ofthe-
art galaxy decompositions, which take into account
%%%
bulge, disks, spiral arms, bars, rings, halo, extended or
unresolved nuclear source and partially depleted core.
%%%
Kinematical information (Emsellem et al. 2011; Scott
et al. 2014; Arnold et al. 2014) was used to conrm the
%%%
presence of rotationally supported disk components in
most early-type (elliptical + lenticular) galaxies, and to
%%%
identify their extent (intermediate-scale disks that are
fully embedded in the bulge, or large-scale disks that encase
%%%
the bulge and dominate the light at large radii).
It is worth stressing that, contrary to common knowledge,
%%%
the majority of elliptical galaxies contain disks,
i.e. they are not single-component spheroidal systems.
%%%
Paper I presents the dataset used here, including details
about the data reduction process and the galaxy modelling
%%%
technique that we developed. It also discusses how
we estimated the uncertainties5 on the bulge magnitudes,
%%%and presents the individual 66 galaxy decompositions,
along with a comparison and discussion of past decompositions.
%%%The morphological classication (E = elliptical; E/S0 =
elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/
%%%
spiral; Sp = spiral; and merger") follows from the
galaxy models presented in Paper I. Throughout this paper
%%%
we will refer to early-type galaxies (E+S0) and latetype
galaxies (Sp). Two galaxies classied as E/S0 are
%%%
obviously included in the early-type bin, whereas two
galaxies classied as S0/Sp and another two classied as
%%%
mergers are included in neither the early- nor the latetype
bin.

@@

\section{Results}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{}
\label{fig:magn}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{}
\label{fig:mbhn}
\end{center}
\end{figure}

>>>>

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample (Table \ref{tab:sample}) used in \emph{Paper II}, 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
associated with their fitted parameters. 
Refer to \emph{Paper I} for a detailed discussion on this. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, here we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes two galaxies classified as E/S0, 
whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - n_{\rm sph}$ diagrams (see Table \ref{tab:lregLn} and Table \ref{tab:lregMn}, respectively) 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict values of the ordinate observable ($Y$) with the best possible precision.

%for different morphological types (elliptical/lenticular/spiral)

\subsection{$L_{\rm sph} - n_{\rm sph}$}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}
